---
title       : Hierarchical clustering
subtitle    : Using the 'mtcars' data set
author      : Stephan
job         : Coursera student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Hierarchical clustering

A short description:  

`In data mining, hierarchical clustering is a method of cluster analysis which seeks to build a hierarchy of clusters`   
`Source: Wikipedia`

--- .class #id 

## The data

We use the `mtcars` data set, as provided by `R`.  
The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).

An extract:
```{r head, echo=FALSE, warning=FALSE, results='asis'}
library(xtable)
print(xtable(head(mtcars)), type="html")
```


---

## The result

Performing hierarchical clustering on the sample data identifies basically four `clusters of car types`:

```{r hc, echo=FALSE, fig.width=14}
clusters <- hclust(dist(scale(mtcars)), method="complete")
cut <- cutree(clusters, 4)
plot(clusters, hang=-1, main="Hierarchical clustering of cars", sub="1973-74 model year", xlab="Cars", ylab="")
rect.hclust(clusters,4)
```


--- 

## The App

The App  
               [Hierarchical clustering on mtcars data set](https://stephan.shinyapps.io/App2/)  
allows for flexible choice of methods and a flexible choice of clusters.

Enjoy!
